What do incoming university students believe about open science practices in

### 2021-12-03 analysis/Manuscript.Rmd
Jen edits, ready to submit?

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Enter postal address here
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au

affiliation:
  - id: '1'
    institution: Flinders University
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University
  - id: '4'
    institution: Swinburne University of Technology

shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
abstract: |
 BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
 RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

@@

```{r setup, include = FALSE}
library(papaja) #install with devtools
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(tidyselect) 
library(broom)

r_refs("r-references.bib")
```

@@

knitr::opts_chunk$set(
  cache.extra = knitr::rand_seed,
  results = 'as.is')
```

@@

# import the metadata
#MW: I've removed the argument lazy = FALSE from the read_csv command which was causing an error for me - I don't think it's an argument used by that function?
metadata <- here::here("data", "students_metadata.csv") %>%
read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>%
filter(!is.na(old_variable))

# relabel the variable names [completed in preprocessing]
# df <- meta_rename(df, metadata = metadata, old = old_variable, new = new_variable)

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @harrisUseReproducibleResearch2018].

@@

<!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology? JB: That'd be great in the 
abstract and discussion?

MW: Cool - I've put that in the conclusion of the discussion along with a link. Hope that looks ok. I don't think we can quite fit it in the abstract with the 200 word limit.
-->

@@

<!--We had a footnote here (below) but given the word limit it might be safely left out unless a reviewer queries it...

^[While the response "queer man" could potentially be coded as
"male", we are aware that some individuals who report gender in this way would
not feel that such reclassification was appropriate. We have retained the original
response in order to provide a faithful representation of the participant's 
self-reported gender.] -->

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

We presented 20 scenarios (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

@@

# c <- metadata %>%
#     filter(scale == "norms")

# add a practice column in metadata

# update this text  
# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>%
#   rename ("OSmost_label" = "ItemText")

@@

knitr::kable(norm_items_wide,
             caption = "Norm and counternorm items",
             align = c('lll'))
```

@@

hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")
```

@@

<!--Bem begins his guide for writing articles as, “There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results. They are rarely the same, and the correct answer is (b).”
MW: I think the Bem paper would work here if students tended to be pro-HARKing but they tended to be against it.
-->

@@

For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource. These questions are available along with our data and analysis code at https://osf.io/fz6ya/?view_only=46705e978a964cf6b872f4203d718fbe

<!---
MW: We still need to upload the data and code there before submitting, but just popping this placeholder in for now.
I guess we'll need to leave out a couple of the files that have identifiable data in them?
I've also uploaded an exported copy of the survey on the OSF project, with author details blinded.
-->

@@

```{r normsinpracticehistogram}

practice_labels <- c(
  available_data = "Data on\nrequest",
  detailed_methodology = "Information\nfor replication",
  harking = "HARKing",
  incomplete_results = "p-hacking",
  open_access = "Open access",
  registered_reports = "Registered reports",
  open_data = "Open data",
  open_materials = "Open\nmaterials",
  preprint_pre = "Preprints",
  preregistration = "Preregistration",
  registered_report = "Registered\nreport"
)

in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10) +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
    facet_wrap(~practice, nrow = 2, labeller = labeller(practice = practice_labels))

```
\
*Figure A*

@@

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Research Development and Support, Flinders University, Bedford Park, 5042
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au

affiliation:
  - id: '1'
    institution: Flinders University, Australia
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University, Australia
  - id: '4'
    institution: Swinburne University of Technology, Australia

shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default

acknowledgement: |
  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
# will enter this manually on the word document

abstract: |
 BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
 OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
 RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

@@

```{r setup, include = FALSE}

library(papaja) #install with devtools
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(tidyselect) 
library(broom)

r_refs("r-references.bib")

@@

knitr::opts_chunk$set(
  cache.extra = knitr::rand_seed,
  results = 'as.is')

@@

# import the metadata

metadata <- here::here("data", "students_metadata.csv") %>%
read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>%
filter(!is.na(old_variable))

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].

@@

@@

@@

Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? JB: I think we have to, don't we?-->
The ten practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

@@

@@

knitr::kable(norm_items_wide,
             caption = "Norm and counternorm items",
             align = c('lll'))

*Note*: Participants responded to each item in the context of the scenario, “Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis.” Responses were provided on a Likert-type response scale ranging from (strongly disagree) to 5 (strongly agree).

@@

# hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")

df %>%
  filter(!is.na(rep_perc)) %>% 
  ggplot(aes(x = rep_perc)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10, colour = "black", fill = "grey") +
    xlab("Percentage") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 11), axis.title = element_text(size = 11))

@@

@@

For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource. These questions are available at https://tinyurl.com/yz76f4s6 [blinded].

@@

```{r normsinpracticehistogram, fig.cap="Histogram of participants' prevalence ratings (%) for each of the norms in practice items. Responses provided on a visual slider from 0% to 100%."}

practice_labels <- c(
  available_data = "Data on\nrequest",
  info_for_rep = "Information\nfor replication",
  harking = "HARKing",
  phack = "p-hacking",
  open_access = "Open access",
  registered_reports = "Registered reports",
  open_data = "Open data",
  open_materials = "Open\nmaterials",
  preprint_pre = "Preprints",
  preregistration = "Preregistration",
  registered_report = "Registered\nreport"
)

in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10, colour = "black", fill = "grey") +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
    facet_wrap(~practice, nrow = 2, labeller = labeller(practice = practice_labels))

*Figure A*

@@

<!-- We have a four references that aren't including the urls. Including here so we can add them to the final document.

O’Grady, C. (2020, December 9). Psychology’s replication crisis inspires ecologists to push for more reliable research. Science. https://www.sciencemag.org/news/2020/12/psychology-s-replication-crisis-inspires-ecologists-push-more-reliable-research

Vazire, S. (2019). Do we want to be credible or incredible? Association for Interdisciplinary Meta-research & Open Science conference, Melbourne. https://osf.io/thm9a/

Yong, E. (2016, March 4). Psychology’s replication crisis can’t be wished away. The Atlantic. https://www.theatlantic.com/science/archive/2016/03/psychologys-replication-crisis-cant-be-wished-away/472272/

Yong, E. (2018, November 19). Psychology’s replication crisis is running out of excuses. The Atlantic. https://www.theatlantic.com/science/archive/2018/11/psychologys-replication-crisis-real/576223/ -->
